Optimizing Abstract$^{\text 2}$ Machines

### 2012-11-09 paper/paper.tex
Initial plot of numbers.
Some more citations.

\documentclass[preprint,onecolumn,9pt]{onecol} %{sigplanconf}
\usepackage{alltt}
\usepackage{amsmath,amsthm}
\usepackage{amssymb}
\usepackage{stmaryrd}
\usepackage{url}

@@

The \emph{abstracting abstract machines}
approach~\cite{dvanhorn:VanHorn2011Abstracting,dvanhorn:VanHorn2012Systematic}
to deriving program analyses provides a straightforward way of
transforming a programming language semantics in the form of an
abstract machine, into a family of abstract interpreters parameterized
over policies for regulating the analytic precision of the control,
environment, store, and base value domains.  By taking a
machine-oriented view of computation, it becomes possible to design,
verify, and implement program analyzers for realistic language
features typically considered difficult to model.  The approach was
originally applied to features such as higher-order functions,
stack-inspection, exceptions, laziness, first-class continuations, and
garbage collection.  It has since been used to verify actor-based
parallelism~\cite{local:DOsualdo:12A} and behavioral
contracts~\cite{FIXME:tobin-hochstadt}; it has been used to model
Dalvik, Erlang~\cite{local:DOsualdo:12B},
JavaScript~\cite{local:DBLP:journals/corr/abs-1109-4467}, Racket, and
Coq~\cite{local:harvard}.

@@

>>>>

\documentclass[preprint,onecolumn,9pt]{sigplanconf} %{onecol} 
\usepackage{alltt}
\usepackage{amsmath,amsthm}
\usepackage{amssymb}
\usepackage{stmaryrd}
\usepackage{url}
\usepackage{graphicx}

@@

The \emph{abstracting abstract machines}
approach~\cite{dvanhorn:VanHorn2011Abstracting,dvanhorn:VanHorn2012Systematic}
to deriving program analyses provides a straightforward way of
transforming a programming language semantics in the form of an
abstract machine, into a family of abstract interpreters parameterized
over policies for regulating the analytic precision of the control,
environment, store, and base value domains.  By taking a
machine-oriented view of computation, it becomes possible to design,
verify, and implement program analyzers for realistic language
features typically considered difficult to model.  The approach was
originally applied to features such as higher-order functions,
stack-inspection, exceptions, laziness, first-class continuations, and
garbage collection.  It has since been used to verify actor-
\cite{local:DOsualdo:12A} and
thread-based~\cite{dvanhorn:Might2011Family} parallelism and
behavioral contracts~\cite{dvanhorn:TobinHochstadt2012Higherorder}; it
has been used to model Dalvik, Erlang~\cite{local:DOsualdo:12B},
JavaScript~\cite{local:DBLP:journals/corr/abs-1109-4467},
Racket~\cite{dvanhorn:TobinHochstadt2012Higherorder}, and
Coq~\cite{local:harvard}.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=6in]{rel-time.ps}
\end{center}
\end{figure*}
